Estimation below the detection limit

### 2018-04-12 TEX/draft2.tex
nothing much

In order to estimate the autocorrelations of the signal, we first compute the first $L$ entries of the data's autocorrelations. 
For the purpose of the analysis, we consider  the asymptomatic regime where $M,N\to\infty$, while preserving fixed ratio. 
Specifically, we define the ratio of the measurement occupied by  the signal as
\begin{equation}
\gamma = \frac{M L}{N}.
\end{equation}
Under the spacing constraint~\eqref{eq:spacing}, we have $\gamma\leq\frac{L}{2L-1}\approx 1/2$.

@@

Here we should say that we can work only with non-biased terms
%\subsection{One-dimensional experiments}

%Here will come the 1D experiment with heterogeneity

>>>>

In order to estimate the autocorrelations of the signal, we first compute the first $L$ entries of the data's autocorrelations. 
For the purpose of the analysis, we consider  the asymptotic regime where $M,N\to\infty$, while preserving fixed ratio. 
Specifically, we define the ratio of the measurement occupied by  the signal as
\begin{equation}
\gamma = \frac{M L}{N}.
\end{equation}
Under the spacing constraint~\eqref{eq:spacing}, we have $\gamma\leq\frac{L}{2L-1}\approx 1/2$.

@@

\TODO{Here we should say that we can afford to work only with non-biased terms}

\subsection{One-dimensional experiments}

Here will come the 1D experiment with heterogeneity
